Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-07-05 latex/ICPP21/paper.tex
add ACM copyright info

\acmConference[ICPP'21]{International Conference on Parallel Processing}{August 9--12}{Chicago, IL, USA}

\title{Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

This material is based upon work supported by the NSF Grant No. 1942892 and a Wake Forest University Undergraduate Research and Creative Activities (URECA) Research Fellowship.

>>>>

\copyrightyear{2021} 
\acmYear{2021} 
\setcopyright{acmcopyright}\acmConference[ICPP Workshops '21]{50th International Conference on Parallel Processing Workshop}{August 9--12, 2021}{Lemont, IL, USA}
\acmBooktitle{50th International Conference on Parallel Processing Workshop (ICPP Workshops '21), August 9--12, 2021, Lemont, IL, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3458744.3474050}
\acmISBN{978-1-4503-8441-4/21/08}

\title{Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms}

@@

This material is based upon work supported by the National Science Foundation Grant No. 1942892 and a Wake Forest University Undergraduate Research and Creative Activities (URECA) Research Fellowship.
